Functions and graphics deliverable
========================================================

```{r}
# How many odds
oddcount <- function(x) {sum((x%%2 == 0)==FALSE)}
```
```{r}
# oddcount Test
oddcount(c(1,2,3,4,5,6,7))
oddcount(c(25,26,39,43,1001,91,33))
oddcount(c(96,20,24,78,100,32))
```{r}
# How many evens
evencount <- function(x) {sum((x%%2) == 0)}
```{r}
# evencount test
evencount(c(1,2,3,4,5,6,7))
evencount(c(25,26,39,43,1001,91,33))
evencount(c(96,20,24,78,100,32))
```
```{r}
# HypothenuseLength
HypothenuseLength <- function(a,b){
c=sqrt(a^2+b^2)
return(c)
}
```

```{r}
# Hypothenuse Length test
HypothenuseLength(4,3)

```

```
```{r}
# LawOfcosine
LawOfcosine <- function(a,b,theta){
c=sqrt(a^2+b^2-2*a*b*cos(theta)) 
return(c)
}
```
```{r}
# LawOfcosine Test
LawOfcosine(13,84,pi/2)
LawOfcosine(2,3,pi/2)
LawOfcosine(3,2,pi/4)
LawOfcosine(3,2,pi/6)
LawOfcosine(3,4,pi/2)
```

```{r}
# Find angle
angleFinder <- function(a,b,c){
theta=acos((c^2-a^2-b^2)/(-2*a*b))
return(theta)
}
```
```{r}
angleFinder(3,4,5)
angleFinder(13,84,85)
angleFinder(3,2,2.125)
```{r}

# Graphics

```{r}
# Circles
circle <- function(x, y, r, ...) {
ang <- seq(0, 2*pi, length = 100)
xx <- x + r * cos(ang)
yy <- y + r * sin(ang)
polygon(xx, yy, ...)
}
```{r}
circle(0,0,5)
```

